### 2019-12-07 article.tex
Some informations about t different images added

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{amsmath}
%\usepackage{mathpazo}

@@

>>>>

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{amsmath}
\usepackage{algorithm2e}
%\usepackage{mathpazo}

@@

As we meant to put temporal data aside, we can assume that the fMRI data for each participant is $t$ different 3D images we had obtained from their brain (despite its time-based sequences). Correspondingly this assumption will multiply our dataset samples by $t (=198)$, enabling us to train our model faster and escape overfitting. On the other hand, in the test phase, our model won't just give binary predictions about a participant being a Parkinson's patient or a healthy control, but it can give us an approximation about the probability of a person being healthy or not. In this step, the trained network will give $t$ different predictions for each person (based on $t$ images) providing a ratio, which corresponds to a probability of healthiness, and we can set a criterion (like $0.5$) to decide if someone belongs to HC class or not.
